---
title: "Template  raulgfc"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

```{r setup, include=FALSE}
library("shiny")
library("flexdashboard")
library ("knitr")

```



Pagina 1 
===================================== 

Inputs {.sidebar}
-------------------------------------
```{r}

``` 
    
Row
-------------------------------------
    
### Quadro 1
    
```{r}

```
Row {tabset .tabset-fade}
-------------------------------------
    
### Quadro 2.1
    
```{r, echo = FALSE}
numericInput("rows", "Entrada Numerica", 0)

```

### Quadro 2.2
    
```{r}

```  

### Quadro 2.3
    
```{r}

```  

### Quadro 2.4
    
```{r}

```  


 
Row 
-------------------------------------
    
### Quadro 3
    
```{r}

```   
    
### Quadro 4

```{r}

```

Row {.tabset .tabset-fade}
-------------------------------------

### Quadro 5.1
    
```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(mtcars[1:5, ], caption = "A knitr kable.")
``` 
    
### Quadro 5.2

```{r}

```

### Quadro 5.3
    
```{r}

```
    
### Quadro 5.4

```{r}

```

Pagina 2 {data-orientation=rows}
===================================== 

---
title: "Chart Stack"
output: flexdashboard::flex_dashboard
---
    
### Quadro 1
    
```{r}
```{r, echo = FALSE}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)

renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)

  # draw the histogram with the specified number of bins
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```
```
    
### Quadro 2

```{r, echo = FALSE}
numericInput("rows", "How many cars?", 5)

renderTable({
  head(cars, input$rows)
})
```



